Vulnerability Analysis of Container Images in Neuroimaging

### 2020-06-03 paper.tex
ordered markers

\change{Container image scanners can be broadly categorized into static and dynamic
scanners. Static scanning performs analysis on a image without running it
as a container. Therefore, commands cannot be executed to inquire installed packages}

\tristan{Does it really look into files, or only installed packages? Please check. The difference is important 
when software is installed without using the package manager.}, without deploying the image in a container. In
dynamic scanning however, a container is started from the image and
\tristan{... It is still unclear how dynamic scanning works. Your text
mentions ``running a container from the image and then scanning the dynamic
behavior of the image'' but in practice it should explain what is executed
in the image: the package manager? other scanning tools? Please clarify by
completing this sentence.}

@@

We used four popular image scanners, namely Anchore~\cite{github_2019},
Vuls~\cite{future-architect_2019}, Clair Scanner~\cite{arminc_2019} and
Stools~\cite{stools}. Anchore, Vuls and Clair Scanner support Docker
images while Stools supports Singularity. Vuls is a dynamic scanner, while the others
are static scanners. To avoid discrepancies, we froze the vulnerability
databases for these scanners on September 25, 2019.

@@

Stools combines CoreOS's Clair Scanner with Continuous Integration (CI)
for scanning Singularity images for vulnerabilities.
Initially, Clair Scanner was intended to scan Docker containers only. This tool does not fit well
to scan Singularity images because of the different image formats.
However, TravisCI and CircleCI are commonly used for testing code, and these
services also offer running containers. Stools combined both these concepts.
It involves spinning a Clair Scanner container during testing and building a
Singularity image, and scanning it for filesystem before the image is finalized.

@@

\begin{table}
\csvreader[%
 respect all,%
  before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
      \begin{adjustbox}{max width=\columnwidth},
  after reading=\end{adjustbox},
 tabular={c |c},
        table head =Singularity Images & {Vulnerabilities by Stools}\\\hline,
 late after line= \\,
        late after last line=\\\hline %\multicolumn{5}{c}{Total Score: 1481}
]{Singularityresults.csv}{}{\csvlinetotablerow}%
       \centering
        \caption{\label{sing}Number of Vulnerabilities in Singularity images}
\end{table}

@@

Table~\ref{sing} shows the number of vulnerabilities present in Singularity
images whereas Figure~\ref{fig:venn} illustrates the number of
vulnerabilities in Docker images, which are detected by the three scanners.
\tristan{You should refer to tables in the order they are presented (1
first, then 2). Tables should also be located next to their reference. In
this case I would actually create a single table, greying out cells that
aren't pertinent (Anchore, Vuls and Clair for Singularity images.)}
 The
overlapping regions of the Venn diagram show the number of common vulnerabilities detected by either two or
three scanners. In total 10691 vulnerabilities are detected by three scanners.
There are also vulnerabilities that are detected only by one scanner. \tristan{The last 3 sentences bring absolutely no 
extra information that can't be read on the figure directly. You should replace them with only 1 sentence noting that there 
are important discrepancies between scanner results (maybe quantify that with a Dice or Jaccard coefficient). This is an example 
of how writing should be improved throughout the paper.}

Figure~\ref{fig:graph1} gives more image-specific information.
It represents the number of vulnerabilities that are present inside images.
The overall trend of the Figure shows that as the number of packages increases in the image, the number of vulnerabilities
also get increased \tristan{mention the parameters of the regression line (preferably as a label in the figure) and the regression error}.
The figure also infers that Alpine distribution, being the
lightweight distribution, have the least number of vulnerabilities, whereas Ubuntu contains the highest number of
vulnerabilities. Debian and Centos contain a higher number of critical vulnerabilities than Ubuntu and Alpine \tristan{I dont think there is enough data to 
claim that, claim should be softened.}.
Similarly, Figure~\ref{sing} \tristan{there is a reference error, and if it's still a different figure I think you should make only 1.} illustrates the number of vulnerabilities in Singularity images used in Boutiques images.
\tristan{In the Figure, could you increase the marker size in the caption, and order it so that the different versions of a distribution 
are grouped together and sorted by increasing version?}
\begin{table*}
\csvreader[%
 respect all,%
  before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
      \begin{adjustbox}{max width=\textwidth},
  after reading=\end{adjustbox},
 tabular={c |c | c | c | c |c},
	table head =Image Labels &{Image names} &{OS Distro} & {Vulnerabilities by Anchore} & {Vulnerabilities by Clair} & {Vulnerabilities by Vuls}\\\hline,
 late after line= \\,
        late after last line=\\\hline %\multicolumn{5}{c}{Total Score: 1481}
]{results.csv}{}{\csvlinetotablerow}%
       \centering
	\caption{\label{table1}Existing number of Vulnerabilities}
\end{table*}
%\begin{comment}
%\begin{table}
%\csvreader[%
% respect all,%
%  before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
%      \begin{adjustbox}{max width=\columnwidth},
%  after reading=\end{adjustbox},
% tabular={c|c},
%	table head ={Image Tag} & {Image Name}\\\hline,
% late after line= \\,
%        late after last line=\\\hline %\multicolumn{5}{c}{Total Score: 1481}
%]{names.csv}{}{\csvlinetotablerow}%
%       \centering
%	\caption{\label{table2}Image names}
%\end{table}
%\end{comment}
\begin{figure}
        {\includegraphics[scale=2.5,width=\columnwidth]
        {Figures/venn.pdf}}
        \caption{\label{fig:venn} Scanner results}
\end{figure}

@@

\begin{figure*}[b]
        {\includegraphics[width=\textwidth]
        {Figures/vulnwithupdate.pdf}}
        \caption{\label{fig:graph2} Numner of vulnerabilities before and
        after update of the images}
      \end{figure*}

@@

Table~\ref{table1} compares the results of scanning images with the three scanners.
Venn Diagram in Figure~\ref{fig:venn} summarizes this table. \tristan{You said it already.}

@@

The number and type of vulnerabilities reported by the three scanners are drastically different from each other.
It was interesting to investigate the reasons for these differences.
%these scanners report different numbers and types of vulnerabilities.
%How their logic differs and what exactly is making these results different than each other.

@@

\textbf{CVEs with Status as “Not-affected”:} Vuls is reporting vulnerabilities that have status
as "not-affected" in the vulnerability database. So it means Linux distribution which is inside the image is not affected
by the particular CVE. However, it is reported by Vuls \tristan{do you mean Anchore? This sounds circular.}. In other words, we can say that
these are false positives \tristan{the use of ``false positives'' is ambiguous} by Vuls.
For example, we scanned an image having the Trusty release in it and Vuls is reporting CVE-2015-2305
in the package Cups. However, if we check the vulnerability database, package Cups in Trusty is not
affected by this CVE.

@@

Our third experiment involves deleting unnecessary packages from the images.
\change{We did this experiment on five images because the reduction process may take
several hours. Size reduction process also requires 
to run a pipeline in the image, which takes time}. We noticed that
after the size reduction process, the scanning results deviate a little from our initial expectation.
At first, we thought that we will have a notable effect of size reduction on
vulnerabilities. However, this is not the case always. The bar graph shown in
Figure~\ref{fig:bargraph} illustrates that images \textit{bids/ndmg} and
\textit{poldracklab/fmriprep:1.2.3} have an insignificant effect of size reduction.
According to our analyzes here, this can be due to two reasons: \rom{1}) the number
and \rom{2}) the kind of packages that we deleted. In other
words, if we delete a low number of packages then vulnerabilities do not get decreased as expected.
In contrast, if the number of deleted packages are high, reduction
in vulnerabilities also becomes high. For instance, we were able to delete only 21 and 25 packages for 
\textit{bids/ndmg} and \textit{poldracklab/fmriprep:1.2.3} images. Consequently, vulnerabilities
reduced only by 4 and 17 respectively. Furthermore, this is illustrated in Figure~\ref{deleted} \tristan{I'm not thrilled by this figure, I would 
just mention in the text that we verified that.}.
\tristan{The next sentence is interesting because it starts characterizing the images that benefit the most 
from size reduction. The previous sentences read like a tautology, you should make your comment more specific.} 
Also, if we delete packages that contain a lot of vulnerabilities, it helps in reducing
vulnerabilities by a significant number. For instance, in case of our experiments
deleting compilers and Linux-kernel-header packages helped to minimize vulnerabilities
by a significant number in \textit{bids/example, bids/freesurfer, and bids/mindboggle:0.0.4-1}. 
%Our third experiment shows that deleting unnecessary packages from the image also helps to reduce
%the number of vulnerabilities by a significant number. We started this experiment with
%\textit{bids/example} image and deleted 61 unnecessary packages out of total 528 packages, which helped
%to reduce 838 vulnerabilities to 523. Later, we also checked with \textit{bids/freesurfer} image, which allowed
%to delete 71 unnecessary packages out of total 298 packages. Consequently, reducing number of vulnerabilities
%from 353 to 101.

@@

Our last experiment includes updating the image and then removing unnecessary packages from it.
Figure~\ref{fig:bargraph} displays the results. 
Our initial thought was that with the update and size reduction process together, we will be able to
reduce vulnerabilities even more. However
we analyzed that this is not always true. Again, it depends on which packages you \tristan{in general don't use ``you'' in a 
formal paper.} are deleting and how
many vulnerabilities they contained. To illustrate, \textit{bids/example} image in Figure~\ref{fig:bargraph}
shows no effect of size reduction along with update process. It has 181 vulnerabilities for both experiments 2 and 4.
Meaning that packages, which we deleted after updating the image, were already vulnerability free. Therefore,
scanning results did not change.

@@

\subsection{Conclusion}

In this paper, we performed various experiments to study the security state of the Docker
and Singularity images, which are used in the neuroimaging field. We found out strong correlation
between the number of packages and the number of vulnerabilities in the images, which implies
that the number of vulnerabilities increases with the number of packages. We also found out that
updating images reduces the number of vulnerabilities by a significant number. However, for some
vulnerabilities there are no fixes available yet so the images cannot 
be made totally invulnerable. Continuing with our next two experiments, we analyzed that the
image size reduction process also reduces vulnerabilities a lot. However, we found out that this is not
always true. It depends on two factors: kind and the number of packages that we are
deleting. Therefore, we conclude this paper by suggesting ten simple rules that can be
followed to keep container images safe.
\newline 1. Update packages regularly.
\newline 2. Remove unnecessary packages, in particular the ones used for installation (compilers, source packages, etc).
\newline 3. Mind your base OS image.
\newline 4. Run image scanning tools in CI scripts. For instance Anchore.
\newline 5. Mind your GitHub/DockerHub credentials.
\newline 6. Minimize dependencies.
\newline 7. Avoid static linking because it obfuscates vulnerability scanning.
\newline 8. Use the package manager to facilitate vulnerability detection.
\newline 9. Use OS releases that have LTS support.
\newline 10. Sign your images.

\tristan{You should discuss future work here too.}

>>>>

\change{Container image scanners can be broadly categorized into static and dynamic
scanners. Static scanning performs analysis on a image without running it
as a container. Therefore, package manager, which is a executable file,
cannot be used to extract required data while statically extracting image data.
Thus, scanners parse different files for extracting image data e.g, installed packages, their versions,
and OS distribution etc. For instance, in Debian and Ubuntu, \textit{/var/lib/dpkg/status} file
can be parsed to get a list of installed packages and in the same way \textit{/etc/os-release} file can be
parsed to get information about OS distribution.
Whereas in dynamic scanning, a container is deployed from the image first and then
package manager of the image is executed inside the container to collect required data.}

@@

\change{We used four popular image scanners, namely Anchore~\cite{github_2019},
Vuls~\cite{future-architect_2019}, Clair Scanner~\cite{arminc_2019} and
Stools~\cite{stools}. Anchore, Vuls and Clair Scanner support Docker
images while Stools supports Singularity. Vuls support both static as well as dynamic
scanning till version 0.9.5, however, in our experiments we used it dynamically.
On the contrary, the others
are static scanners.} To avoid discrepancies, we froze the vulnerability
databases for these scanners on September 25, 2019.

@@

Stools combines CoreOS's Clair Scanner with Continuous Integration (CI)
for scanning Singularity images for vulnerabilities.
Initially, Clair Scanner was intended to scan Docker images only. This tool does not fit well
to scan Singularity images because of the different image formats.
However, TravisCI and CircleCI are commonly used for testing code, and these
services also offer running containers. Stools combined both these concepts.
It involves spinning a Clair Scanner container during testing and building a
Singularity image, and scanning it for filesystem before the image is finalized.

@@

%\begin{table}
%\csvreader[%
% respect all,%
%  before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
%      \begin{adjustbox}{max width=\columnwidth},
%  after reading=\end{adjustbox},
% tabular={c |c},
%        table head =Singularity Images & {Vulnerabilities by Stools}\\\hline,
% late after line= \\,
%        late after last line=\\\hline %\multicolumn{5}{c}{Total Score: 1481}
%]{Singularityresults.csv}{}{\csvlinetotablerow}%
%       \centering
%        \caption{\label{sing}Number of Vulnerabilities in Singularity images}
%\end{table}

@@

Table~\ref{table1} shows the number of vulnerabilities present in the images,
which are detected by the scanners.
\tristan{You should refer to tables in the order they are presented (1
first, then 2). Tables should also be located next to their reference.}
It is important to note that results have major discrepancies.
The Jaccard coefficient of Anchore with both Clair and Vuls is 0.59,
whereas Vuls and Clair have 0.83.

Figure~\ref{fig:graph1} gives more image-specific information.
It represents the number of vulnerabilities that are present inside images.
The overall trend of the Figure shows that as the number of packages increases in the image, the number of vulnerabilities
also get increased \tristan{mention the parameters of the regression line (preferably as a label in the figure) and the regression error}.
The figure also infers that Alpine distribution, being the
lightweight distribution, have the least number of vulnerabilities, whereas Ubuntu contains the highest number of
vulnerabilities. Debian and Centos contain a higher number of critical vulnerabilities than Ubuntu and Alpine \tristan{I dont think there is enough data to 
claim that, claim should be softened.}.
%\begin{table*}
%\csvreader[%
% respect all,%
%  before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
%      \begin{adjustbox}{max width=\textwidth},
%  after reading=\end{adjustbox},
% tabular={c |c | c | c | c |c},
%	table head =Image Labels &{Image names} & {OS} & {Anchore} & {Clair} & {Vuls}\\\hline,
% late after line= \\,
%        late after last line=\\\hline %\multicolumn{5}{c}{Total Score: 1481}
%]{results.csv}{}{\csvlinetotablerow}%
%       \centering
%	\caption{\label{table1}Existing number of Vulnerabilities}
%\end{table*}

\begin{table*}[!ht]
\csvreader[%
 respect all,%
  before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
      \begin{adjustbox}{max width=\textwidth},
  after reading=\end{adjustbox},
 tabular={c |c | c | c | c |c},
	table head =Image Labels &{Image names} & {Anchore} & {Clair} & {Vuls} &{Stools}\\\hline,
 late after line= \\,
        late after last line=\\\hline %\multicolumn{5}{c}{Total Score: 1481}
]{fullresults.csv}{}{\csvlinetotablerow}%
       \centering
        \caption{\label{table1}Number of vulnerabilities by scanners}
\end{table*}

\begin{figure}
        {\includegraphics[scale=2.5,width=\columnwidth]
        {Figures/venn.pdf}}
        \caption{\label{fig:venn} Scanner results}
\end{figure}

@@

\begin{figure*}[b]
        {\includegraphics[width=\textwidth]
        {Figures/vulnwithupdate.pdf}}
        \caption{\label{fig:graph2} Number of vulnerabilities before and
        after update of the images}
      \end{figure*}

@@

@@

As the number and type of vulnerabilities reported by the three scanners are drastically different from each other,
it was interesting to investigate the reasons for these differences.
%these scanners report different numbers and types of vulnerabilities.
%How their logic differs and what exactly is making these results different than each other.

@@

\textbf{CVEs with Status as “Not-affected”:} Vuls is reporting vulnerabilities that have status
as "not-affected" in the vulnerability database. It means Linux distribution which is inside the image is not affected
by the particular CVE. In other words, Vuls is reporting vulnerabilities that it should not have reported.
For example, we scanned an image having the Trusty release in it and Vuls is reporting CVE-2015-2305
in the package Cups. However, if we check the vulnerability database, package Cups in Trusty is not
affected by this CVE.

@@

Our third experiment involves deleting unnecessary packages from the images.
\change{We did this experiment on five images because the reduction process may take
several hours because it requires 
a pipeline to run in the image, which takes time. We noticed that
after the size reduction process, the scanning results deviate a little from our initial expectation.
At first, we thought that we will have a notable effect of size reduction on
vulnerabilities. However, this is not the case always. The bar graph shown in
Figure~\ref{fig:bargraph} illustrates that images \textit{bids/ndmg} and
\textit{poldracklab/fmriprep:1.2.3} have an insignificant effect of size reduction.
According to our analyzes here, this can be due to two reasons: \rom{1}) the number
and \rom{2}) the kind of packages that we deleted. In other
words, deleting more packages reduces more vulnerabilities. 
For instance, we were able to delete only 21 and 25 packages for 
\textit{bids/ndmg} and \textit{poldracklab/fmriprep:1.2.3} images. Consequently, vulnerabilities
reduced only by 4 and 17 respectively. 
Also, if we delete packages that contain a lot of vulnerabilities, it helps in reducing
vulnerabilities by a significant number. For instance, in case of our experiments
deleting compilers and Linux-kernel-header packages helped to minimize vulnerabilities
by a significant number in \textit{bids/example, bids/freesurfer, and bids/mindboggle:0.0.4-1}.} 
%Our third experiment shows that deleting unnecessary packages from the image also helps to reduce
%the number of vulnerabilities by a significant number. We started this experiment with
%\textit{bids/example} image and deleted 61 unnecessary packages out of total 528 packages, which helped
%to reduce 838 vulnerabilities to 523. Later, we also checked with \textit{bids/freesurfer} image, which allowed
%to delete 71 unnecessary packages out of total 298 packages. Consequently, reducing number of vulnerabilities
%from 353 to 101.

@@

Our last experiment includes updating the image and then removing unnecessary packages from it.
Figure~\ref{fig:bargraph} displays the results. 
Our initial thought was that with the update and size reduction process together, we will be able to
reduce vulnerabilities even more. However,
we analyzed that this is not always true. Again, it depends on which packages are deleted and how
many vulnerabilities they contained. To illustrate, \textit{bids/example} image in Figure~\ref{fig:bargraph}
shows no effect of size reduction along with update process. It has 181 vulnerabilities for both experiments 2 and 4.
Meaning that packages, which we deleted after updating the image, were already vulnerability free. Therefore,
scanning results did not change.

@@

\subsection{Conclusions and Future Work}

In this paper, we performed various experiments to study the security state of the Docker
and Singularity images, which are used in the neuroimaging field. We found out strong correlation
between the number of packages and the number of vulnerabilities in the images, which implies
that the number of vulnerabilities increases with the number of packages. We also found out that
updating images reduces the number of vulnerabilities by a significant number. However, for some
vulnerabilities there are no fixes available yet so the images cannot 
be made totally invulnerable. Continuing with our next two experiments, we analyzed that the
image size reduction process also reduces vulnerabilities a lot. However, we found out that this is not
always true. It depends on two factors: kind and the number of packages that we are
deleting. Therefore, we conclude this paper by suggesting some particular rules that can be
followed to keep container images safe.
\newline 1. Update packages regularly.
\newline 2. Remove unnecessary packages, in particular the ones used for installation (compilers, source packages, etc).
\newline 3. Mind your base OS image.
\newline 4. Run image scanning tools in CI scripts. For instance Anchore.
\newline 5. Mind your GitHub/DockerHub credentials.
\newline 6. Minimize dependencies.
\newline 7. Avoid static linking because it obfuscates vulnerability scanning.
\newline 8. Use the package manager to facilitate vulnerability detection.
\newline 9. Use OS releases that have LTS support.
\newline 10. Sign your images.

In future work we would like to see how these vulnerabilities can be leveraged
to design attacks from containers. Particularly, we want
to consider web servers and clusters that processes data using containers.

\tristan{future work}
